### 2022-12-15 paper.tex
h

where $\omega=kc$. If $\d p/\d r$ is small, we can divide the region $r> R$ into many spherical shells, and in each of them $p$ is nearly constant. To make $f(r,t)$ continuous anytime, we suppose that the ``angular frequency'' $\omega$ in each shell is same, and then there will be a approximate solution
\begin{equation}\label{solution}

@@

If $p$ is small, \eqref{solution} can be approximated to

@@

then wave of $\vec{E}$ and $\vec{H}$ will approximately arrive Earth at the same time, and also $rE \propto e^{\int(\frac{\d}{\d r}(\ln\mu_{\text{G}})/2)\d r} \propto \mu_{\text{G}}^{1/2}$, $rH\propto e^{\int(\frac{\d}{\d r}(\ln\varepsilon_{\text{G}})/2)\d r} \propto \varepsilon_{\text{G}}^{1/2}$.

>>>>

where $\omega=kc$. If $\d p/\d r$ is small, we can divide the region $r> R$ into many spherical shells, and in each of them $p$ is nearly constant. To make $f(r,t)$ continuous anytime, we suppose that the ``angular frequency'' $\omega$ in each shell is the same, and then there will be a approximate solution
\begin{equation}\label{wave_solution}

@@

If $p$ is small, \eqref{wave_solution} can be approximated to

@@

then wave of $\vec{E}$ and $\vec{H}$ will approximately arrive Earth at the same time, and also $rE \propto e^{\int(\frac{\d}{\d r}(\ln\mu_{\text{G}})/2)\d r} \propto \mu_{\text{G}}^{1/2}$, $rH\propto e^{\int(\frac{\d}{\d r}(\ln\varepsilon_{\text{G}})/2)\d r} \propto \varepsilon_{\text{G}}^{1/2}$. Again, if $p$ is small, $\left\lvert i(\omega/c)\int f\d r\right\rvert \approx\left\lvert \frac{\p}{\p r}\int f\d r\right\rvert $ and $-i\omega\int f\d t=\frac{\p}{\p t}\int f\d t$. Since $\vec{H}=\mu_\text{G}^{-1}\vec{\nabla}\times\vec{A}$ and $H\propto \varepsilon_\text{G}^{1/2}/r$, $\mu_\text{G}^{-1}(\omega/c)A\propto\varepsilon_{\text{G}}^{1/2}/r\Rightarrow A\propto \mu_\text{G}^{1/2}/r$. Since $\vec{E}=-\vec{\nabla}\varphi-\frac{\p}{\p t}\vec{A}$, $E\propto \mu_\text{G}^{1/2}/r$ and $\frac{\p}{\p t}\vec{A}\propto \omega\mu_\text{G}^{1/2}/r\propto \mu_\text{G}^{1/2}/r$, $(\omega/c)\varphi\propto\mu_\text{G}^{1/2}/r\Rightarrow \varphi/c\propto\mu_\text{G}^{1/2}/r$. Therefore, $\bar{h}_{0 \mu}=-4(\varphi/c,\vec{A})/c\propto\mu_\text{G}^{1/2}/cr\propto G^{1/2}/c^2r$.
